---
output:
  md_document:
    variant: gfm
html_preview: false
---


```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
library("yulab.utils")
```


# DOSE: Disease Ontology Semantic and Enrichment analysis

`r badge_bioc_release("DOSE", "green")`
`r badge_devel("guangchuangyu/DOSE", "green")`
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/DOSE.svg)](https://www.bioconductor.org/packages/devel/bioc/html/DOSE.html#since)
[![codecov](https://codecov.io/gh/GuangchuangYu/DOSE/branch/master/graph/badge.svg)](https://codecov.io/gh/GuangchuangYu/DOSE/)



[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![platform](http://www.bioconductor.org/shields/availability/devel/DOSE.svg)](https://www.bioconductor.org/packages/devel/bioc/html/DOSE.html#archives)
[![Build Status](http://www.bioconductor.org/shields/build/devel/bioc/DOSE.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/DOSE/)
`r badge_bioc_download("GOSemSim", "total", "blue")`
`r badge_bioc_download("GOSemSim", "month", "blue")`


```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('DOSE')$Description)
```


## :writing_hand: Authors

Guangchuang YU  <https://yulab-smu.top>

School of Basic Medical Sciences, Southern Medical University


Learn more at <https://yulab-smu.top/contribution-knowledge-mining/>.

Please cite the following article when using `DOSE`:

```{r comment="", echo=FALSE, results='asis'}
cat(yulab.utils:::ref_knownledge()["DOSE"], ".\n", sep="")
```
